Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
Addressed a comment from Marcelo

\lbrack{}Additional cleansing\rbrack{}~We noticed that some of the
tests we found depend on external libraries, which not all selected
engines support. We decided to discard those. For example, many tests
we found were based on Node.js~\cite{node} which\Mar{@Igor, is this
  the reason?  Please, confirm$\rightarrow$} require libraries to be
installed before running the test and different tests require
different sets of libraries. Also, as already mentioned, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.  Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due\Mar{@Gustavo/@Breno, we can mention in the
  author response that we did sanity/diligence check.}.

>>>>

\lbrack{}Additional cleansing\rbrack{}~We noticed that some of the
tests we found depend on external libraries, which not all selected
engines support. We decided to discard those. For example, many tests
we found were based on Node.js~\cite{node} which\Mar{@Igor, is this
  the reason?  Please, confirm$\rightarrow$} require libraries to be
installed before running the test and different tests require
different sets of libraries. Also, as already mentioned, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.  Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due.
